\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-01-11 paper.tex
Update the color of the points and consistant with coloring

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, sharp corners]}{\end{tcolorbox}}\fi

@@

\hypertarget{total-number-of-bins}{%
\subsection{Total number of bins}\label{total-number-of-bins}}

@@

\hypertarget{benchmark-value-to-remove-low-density-hexagons}{%
\subsection{Benchmark value to remove low-density
hexagons}\label{benchmark-value-to-remove-low-density-hexagons}}

@@

\hypertarget{benchmark-value-to-remove-long-edges}{%
\subsection{Benchmark value to remove long
edges}\label{benchmark-value-to-remove-long-edges}}

@@

\hypertarget{sec-summary}{%
\subsection{Summaries of the model}\label{sec-summary}}

@@

The concept of ``residuals'' is pivotal in evaluating the accuracy of
representing bin centroids in high dimensions. To quantify this
accuracy, we introduce an error metric, which measures the sum of
squared differences between the high-dimensional data ((x\_\{ij\})) and
the predicted bin centroid data in high-dimensional space
((C\_\{x\_ij\})) across all bins and dimensions. Mathematically, this
error is expressed as:

@@

Here, (n) represents the number of bins, (p) represents the dimensions,
(x\_\{ij\}) is the actual high-dimensional data, and (C\_\{x\_ij\}) is
the predicted bin centroid data in high dimensions.

@@

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, breakable, enhanced]}{\end{tcolorbox}}\fi

@@

\hypertarget{total-number-of-bins}{%
\subsubsection{Total number of bins}\label{total-number-of-bins}}

@@

\hypertarget{benchmark-value-to-remove-low-density-hexagons}{%
\subsubsection{Benchmark value to remove low-density
hexagons}\label{benchmark-value-to-remove-low-density-hexagons}}

@@

\hypertarget{benchmark-value-to-remove-long-edges}{%
\subsubsection{Benchmark value to remove long
edges}\label{benchmark-value-to-remove-long-edges}}

@@

\hypertarget{sec-summary}{%
\subsection{Model summaries}\label{sec-summary}}

@@

The concept of ``residuals'' is pivotal in evaluating the accuracy of
representing bin centroids in high dimensions. To quantify this
accuracy, we introduce an error metric, which measures the sum of
squared differences between the high-dimensional data (\(x_{ij}\)) and
the predicted bin centroid data in high-dimensional space (\(C_{x_ij}\))
across all bins and dimensions. Mathematically, this error is expressed
as:

@@

Here, \(n\) represents the number of bins, \(p\) represents the
dimensions, \(x_{ij}\) is the actual high-dimensional data, and
\(C_{x_ij}\) is the predicted bin centroid data in high dimensions.

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-nldervisUMAP-1.pdf}

\caption{\label{fig-nldervisUMAP}2D layouts from UMAP applied for the
S-curve data: (a) UMAP (n\_neighbors = 7), (b) UMAP (n\_neighbors = 15),
(c) UMAP (n\_neighbors = 32), (d) UMAP (n\_neighbors = 50). Is there a
best parameter choice in representing UMAP or are they all providing
equivalent information?}
